# Introduction {#intro}



## T1

Endoscopic therapy likely sufficient[Pech Gastroenterology  2014 146:652]

See MOlina JTCVS 153:1206


## T2N0

Neoadjuvant chemo not likey to be helpful for early stage disease - FFCD 9901 [Mariette 2416]
Meta-analysis of 5265 patients in 10 studies showed that while neoadjuvant therapy was associated with a reduction in positive margin rate, there was no difference in terms of recurrence or survival.[MOta 176]


French trial FREGAT[Markar 59]
[Speicher 1195]

## Surgery

High volume  Birkmeyer 2117;Wouters 1789;dikken 4068

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

