--- 
title: "GI Cancer Treatment"
author: "Jonathan C Salo MD"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [XPS.bib]
biblio-style: apalike
link-citations: yes
description: "This is an abbreviated (and opinionated) approach to esophageal cancer staging and treatment, designed to provide practical guidance"
---


# (PART\*) Esophageal Cancer {-}

# Introduction {-}

```{r eval=FALSE, echo=F}
install.packages("bookdown")
# or the development version
 #devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE,echo=F}
# automatically create a bib database for R packages
#knitr::write_bib(c(
#  .packages(), 'bookdown', 'knitr', 'rmarkdown'
#), 'packages.bib')
```

This is an abbreviated guide to treatment protocols at the Levine Cancer Institute. They are designed to provide referring physicians and our trainees with general guidelines.  In most cases, these cases are best cared for in a multi-disciplinary environment. Caring for patients with GI cancers is clearly a 'team support' making use of the wisdom and experience of a broad-based teams of practitioners. These guidelines are not presented as 'Standard of Care.' Readers interested in 'Standard of Care' treatment protocols are referred to the National Comprehensive Cancer Network (NCCCN) Guidlines, which can be found at NCCN.org.